---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# vmapp2017

Data package for "[Voluntary action alters the perception of visual illusions](https://link.springer.com/article/10.3758%2Fs13414-017-1321-x)", published in Attention, Perception & Psychophysics (Vuorre & Metcalfe, 2017).

The files are contained in [this GitHub repository](https://github.com/mvuorre/vmapp2017). The data can be downloaded as .csv files from the `data-raw` folder. It can also be installed as an R package directly from R:

```{r}
# install.packages("devtools")  # Install this package if needed
devtools::install_github("mvuorre/vmapp2017")
library(vmapp2017)
```

Once the `vmapp2017` is loaded into the workspace, you can directly access the visual illusion data in the `illusion` variable.

```{r}
head(illusion)
```

The interval estimation data (Experiment 1b) is in an object called `ie`

```{r}
head(ie)
```

The data files are described on their R help pages, or in "Reference", on top of this page.

The data analysis is fully described in "Articles -> Data Analysis" on top of this page.

Citation:

```{r}
citation("vmapp2017")
```
