---
title: "Data Analysis for V&M (2017)"
author: "Matti Vuorre"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, results = "hide", message = F}
library(knitr)
library(gridExtra)
library(lme4)
library(tidyverse)
library(brms)
library(vmapp2017)
knitr::opts_chunk$set(message = F)
```

# Functions and constants

```{r}
get_pse <- function(X, x, c, scale = 1) {
    # Function to get PSEs 
    # X = Matrix of posterior samples (or row of MLEs)
    # x = condition (0 or 1)
    # c = constant (what value ISI is centered on)
    pse <- - ( (X[,1] + X[,3]*x) / (X[,2] + X[,4]*x) )
    pse <- (scale * pse) + c
    return(pse)
}

iters <- 17500
warmups <- 5000
color_vals = c("#e41a1c", "#377eb8")
alphas <- .2

# Estimated models are saved in a local file to save time
load(file="../../../~$models.rda")
```

Use common plotting theme

```{r}
library(vmisc)
theme_set(theme_pub())
```

# Data preparation

The data is contained in this package. Here we collapse the illusion data to counts (models estimate faster with collapsed data)

```{r}
data(illusion)
illusion <- illusion %>% 
    group_by(exp, id, condition, cond, interval) %>% 
    summarise(k = sum(response, na.rm=T),
              n = n(),
              exclude = unique(exclude)) %>% 
    ungroup()
```

# Experiment 1

## Apparent Motion

```{r}
( exp1 <- filter(illusion, exp == 1) )
```

```{r, echo=F}
e1p1 <- exp1 %>% 
    filter(exclude == FALSE) %>%
    ggplot(aes(x=interval, y=k/n, col=condition)) +
    scale_color_manual(values = color_vals) +
    geom_line(size=.5) +
    geom_point() +
    scale_y_continuous(breaks=c(0, 0.5, 1),
                       labels=c("0", ".5", "1")) +
    labs(x="Inter-stimulus interval (ms)", y="Perceived motion") +
    facet_wrap("id", nrow=4)
e1p2 <- e1p1 %+% filter(exp1, exclude == TRUE)
grid.arrange(
    e1p1 + ggtitle("A)"),
    e1p2 + ggtitle("B)") +
        theme(axis.title = element_text(colour = "white"),
              axis.text = element_text(colour = "white")),
    widths = c(8, 2))
```

We reject the participants in B.

```{r}
exp1 <- filter(exp1, exclude == F)
Cc <- mean(unique(exp1$interval))
exp1$isic <- ( exp1$interval - Cc ) / 10
```

### GLMM MLE estimation

```{r, eval = F}
exp1mle <- glmer(k/n ~ isic*condition + (isic*condition|id),
                 weights = n, family=binomial(link=logit), 
                 data=exp1)
```

```{r}
summary(exp1mle)
```

### GLMM Bayes estimation

```{r}
Priors <- c(
    set_prior("normal(0, 100)", class = "b"),
    set_prior("cauchy(0, 4)", class = "sd")
)
```

```{r, message=F, eval = F}
exp1b <- brm(k | trials(n) ~ isic*condition + (isic*condition|id),
             family=binomial(link=logit), prior = Priors,
             data=exp1, cores = 4, iter = iters, warmup = warmups)
```

```{r, echo=F}
Pars <- parnames(exp1b)[1:4]
print(exp1b$fit, pars = Pars, probs = c(0.025, 0.975))
```

```{r}
# Posterior probability (one-sided p-value)
mean(posterior_samples(exp1b, pars = "b_cond") > 0) * 100.0
```

Population level PSEs

```{r, echo=F}
post <- posterior_samples(exp1b, pars = "b")
exp1pse <- tibble(
    Involuntary = get_pse(post, 0, Cc, 10),
    Voluntary = get_pse(post, 1, Cc, 10)) %>%
    mutate(Difference = Voluntary - Involuntary) %>%
    gather()
exp1psesum <- group_by(exp1pse, key) %>%
    summarise(m = mean(value),
              lwr = quantile(value, probs=.025),
              upr = quantile(value, probs=.975))
exp1psesum
group_by(exp1pse, key) %>%
    summarize(pp = mean(value > 0))
```

### Plot results

```{r, echo=F, message = F}
e1p3 <- expand.grid(
    isic = seq(min(exp1$isic), max(exp1$isic), length = 32),
    n = 1,
    condition = c("involuntary", "voluntary")) %>%
    bind_cols(., fitted(exp1b, 
                        newdata = ., 
                        re_formula=NA, 
                        scale = "response") %>%
                  as_tibble()
              ) %>%
    mutate(interval = 10*isic + Cc) %>%
    as_tibble() %>%
    ggplot(aes(x=interval)) +
    scale_color_manual(values = color_vals) +
    scale_fill_manual(values = color_vals) +
    geom_ribbon(aes(ymin=`2.5%ile`, 
                    ymax=`97.5%ile`, 
                    fill=factor(condition)),
                alpha=alphas, col=NA) +
    geom_line(aes(y=Estimate, col=factor(condition), lty=factor(condition)),
              size=1.35) +
    scale_x_continuous(expand = c(0, 0.001)) +
    scale_y_continuous(breaks = c(0, .25, .5, .75, 1),
                       labels = c("0", ".25", ".5", ".75", "1"),
                       limits = c(0, 1), expand = c(0, 0.001)) +
    labs(x="Inter-stimulus interval (ms)", 
         y="Pr(motion)")
```

```{r, message=F}
e1p4 <- ggplot(exp1psesum, aes(x=reorder(key, rev(m)), m)) +
    geom_hline(yintercept = 0, lty=2) +
    geom_point(size=2) +
    geom_errorbar(aes(ymin=lwr, ymax=upr), width = .2, size=.5) +
    scale_y_continuous("PSE (ms)", 
                       breaks = c(-30, 0, 30, 60, 90, 120, 150),
                       limits = c(-35, 155)) +
    scale_x_discrete("Condition", 
                     labels = c("Voluntary", "No action", "Difference"))
```

```{r, message=F, echo=F}
e1p5 <- grid.arrange(
    e1p3 + 
        ggtitle("A)") +
        theme(plot.margin = unit(c(3,2,3,3), "mm"),
              title = element_text(vjust=-.2, hjust=-.1),
              axis.title = element_text(vjust=0.5, hjust=.5)),
    e1p4 + 
        ggtitle("B)") +
        theme(plot.margin = unit(c(3,3,3,2), "mm"),
              title = element_text(vjust=-.2, hjust=-.15),
              axis.title = element_text(hjust=.5)),
    widths = c(.65, .35))
```

Throughout, we use red to refer to the passive observation condition, and blue to the voluntary action condition.

```{r, echo=F}
bind_cols(exp1, as_tibble(fitted(exp1b))) %>%
    ggplot(aes(x=interval, y=k/n, fill=condition)) +
    scale_color_manual(values = color_vals) +
    geom_point(aes(col=condition)) +
    geom_ribbon(aes(ymin=`2.5%ile`/n, ymax=`97.5%ile`/n), alpha = .3) +
    geom_line(aes(y=Estimate/n, col=condition)) +
    facet_wrap("id")
```

## Interval Estimation

```{r}
data(ie)
ie$isic <- ( ie$interval - mean(unique(ie$interval)) ) / 10
ie
```

### LMM MLE 

```{r, eval = F}
iemle <- lmerTest::lmer(estimate ~ isic*condition + (isic*condition|id),
               data = ie)
```

```{r}
summary(iemle)
```

### LMM Bayes

```{r, message=F, eval = F}
ieb <- brm(estimate ~ isic*condition + (isic*condition|id),
           data=ie, cores = 4, iter = iters, warmup = warmups)
```

```{r, echo=F}
print(ieb$fit, pars = Pars, probs = c(0.025, 0.975))
```

```{r}
# Posterior probability (one-sided p-value)
mean(posterior_samples(ieb, pars = "b_cond") < 0) * 100
```

### Plot results

```{r, echo=F}
e1bp5 <- expand.grid(
    isic = sort(unique(ie$isic)),
    condition = c("involuntary", "voluntary")) %>%
    bind_cols(., fitted(ieb, 
                        newdata = ., 
                        re_formula=NA, 
                        scale = "response") %>%
                  as_tibble()
              ) %>%
    mutate(interval = 10*isic + mean(ie$interval)) %>%
    as_tibble() %>%
    ggplot(aes(x=interval)) +
    scale_color_manual(values = color_vals) +
    scale_fill_manual(values = color_vals) +
    geom_ribbon(aes(ymin=`2.5%ile`, 
                    ymax=`97.5%ile`, 
                    fill=factor(condition)),
                alpha=alphas, col=NA) +
    geom_line(aes(y=Estimate, col=factor(condition), lty=factor(condition)),
              size=1.35) +
    scale_x_continuous(breaks = c(50, 150, 250, 350), expand = c(0.002, 0.002)) +
    scale_y_continuous(limits = c(50, 450), expand = c(0, 0.001)) +
    labs(x="Inter-stimulus interval (ms)", 
         y="ISI estimate")
```

```{r}
new_int <- sort(unique(ie$isic))
iepost <- posterior_samples(ieb, pars=parnames(ieb)[1:4])
diffdat <- expand.grid(intrcpt = 0,
                      isic = 0,
                      condition = 1,
                      intrct = new_int)
# create predictor matrix
Xmat <- as.matrix(diffdat)
# matrix for fitted values
fitmat <- matrix(ncol=nrow(iepost), nrow=nrow(diffdat))
# obtain predicted values for each row
for (i in 1:nrow(iepost)) {
    fitmat[,i] <- Xmat %*% as.matrix(iepost)[i,]
}
# get quantiles to plot
diffdat$lower <- apply(fitmat, 1, quantile, prob=0.025)
diffdat$med <- apply(fitmat, 1, quantile, prob=0.5)
diffdat$upper <- apply(fitmat, 1, quantile, prob=0.975)
diffdat$variable <- sort(unique(ie$isic))

e1bp6 <- ggplot(diffdat, aes(x = variable, y=med)) +
    geom_hline(yintercept = 0, lty=2) +
    geom_point(size = 1.4) +
    geom_errorbar(aes(ymin=lower, ymax=upper), width = 1.3, size=.3) +
    scale_y_continuous("Difference (ms)", 
                       breaks = c(20, 0, -20, -40, -60, -80),
                       limits = c(-85, 25)) +
    scale_x_continuous("ISI (ms)", 
                     breaks = c(-15, -5, 5, 15),
                     labels = c("50", "150", "250", "350"),
                     limits = c(-18, 18))
```

```{r}
e1bp7 <- grid.arrange(
    e1bp5 + 
        ggtitle("A)"),
    e1bp6 + 
        ggtitle("B)"),
    widths = c(7, 3))
```

```{r, echo=F}
group_by(ie, id, isic, interval, condition) %>%
    summarize(estimate = mean(estimate)) %>%
    bind_cols(., as_tibble(fitted(ieb, .))) %>%
    ggplot(aes(x=interval, y=estimate, fill=condition)) +
    scale_color_manual(values = color_vals) +
    geom_point(aes(col=condition)) +
    geom_ribbon(aes(ymin=`2.5%ile`, ymax=`97.5%ile`), alpha = .3) +
    geom_line(aes(y=Estimate, col=condition)) +
    facet_wrap("id")
```

# Experiment 2

```{r}
( exp2 <- filter(illusion, exp == 2) )
```

```{r, echo=F}
e2p1 <- exp2 %>% 
    filter(exclude == FALSE) %>%
    ggplot(aes(x=interval, y=k/n, col=condition)) +
    scale_color_manual(values = color_vals) +
    geom_line(size=.5) +
    geom_point() +
    scale_y_continuous(breaks=c(0, 0.5, 1),
                       labels=c("0", ".5", "1")) +
    labs(x="Inter-stimulus interval (ms)", y="Perceived element motion") +
    facet_wrap(~id, nrow=5)
e2p2 <- e2p1 %+% filter(exp2, exclude == TRUE)
grid.arrange(
    e2p1 + ggtitle("A)"),
    e2p2 + ggtitle("B)") +
        theme(axis.title = element_text(colour = "white"),
              axis.text = element_text(colour = "white"),
              aspect.ratio = 1),
    widths = c(8, 2))
```

We reject the participants in B.

```{r}
exp2 <- filter(exp2, exclude == F)
Cc <- 50  # ISI to center on (around middle)
exp2$isic <- ( exp2$interval - Cc ) / 10
```

### GLMM MLE estimation

```{r, eval = F}
exp2mle <- glmer(k/n ~ isic*condition + (isic*condition|id),
                 weights=n, family=binomial(link=logit), 
                 data=exp2)
```

```{r}
summary(exp2mle)
```

### GLMM Bayes estimation

```{r, eval = F}
exp2b <- brm(k | trials(n) ~ isic*condition + (isic*condition|id),
             family=binomial(link=logit), prior = Priors,
             data=exp2, cores = 4, iter = iters, warmup = warmups)
```

```{r, echo=F}
print(exp2b$fit, pars = Pars, probs = c(0.025, 0.975))
```

```{r}
# Posterior probability (one-sided p-value)
mean(posterior_samples(exp2b, pars = "b_cond") > 0) * 100
```

Population-level PSEs.

```{r, echo=F}
post <- posterior_samples(exp2b, pars = "b")
exp2pse <- tibble(
    Involuntary = get_pse(post, 0, Cc, 10),
    Voluntary = get_pse(post, 1, Cc, 10)) %>%
    mutate(Difference = Voluntary - Involuntary) %>%
    gather()
exp2psesum <- group_by(exp2pse, key) %>%
    summarise(m = mean(value),
              lwr = quantile(value, probs=.025),
              upr = quantile(value, probs=.975))
exp2psesum
group_by(exp2pse, key) %>%
    summarize(pp = mean(value > 0))
```

### Plot results

```{r, message=F, echo=F}
e2p3 <- expand.grid(
    isic = seq(min(exp2$isic), max(exp2$isic), length = 32),
    n = 1,
    condition = c("involuntary", "voluntary")) %>%
    bind_cols(., fitted(exp2b, 
                        newdata = ., 
                        re_formula=NA, 
                        scale = "response") %>%
                  as_tibble()
              ) %>%
    mutate(interval = 10*isic + Cc) %>%
    as_tibble() %>%
    ggplot(aes(x=interval)) +
    scale_color_manual(values = color_vals) +
    scale_fill_manual(values = color_vals) +
    geom_ribbon(aes(ymin=`2.5%ile`, 
                    ymax=`97.5%ile`, 
                    fill=factor(condition)),
                alpha=alphas, col=NA) +
    geom_line(aes(y=Estimate, col=factor(condition), lty=factor(condition)),
              size=1.35) +
    scale_x_continuous(breaks = sort(unique(exp2$interval)),
                       expand = c(0, 0.001)) +
    scale_y_continuous(breaks = c(0, .25, .5, .75, 1),
                       labels = c("0", ".25", ".5", ".75", "1"),
                       limits = c(0, 1), expand = c(0, 0.001)) +
    labs(x="Inter-stimulus interval (ms)", 
         y="Pr(element motion)")
```

```{r, echo=F}
e2p4 <- ggplot(exp2psesum, aes(x=reorder(key, rev(m)), m)) +
    geom_hline(yintercept = 0, lty=2) +
    geom_point(size=2) +
    geom_errorbar(aes(ymin=lwr, ymax=upr), width = .2, size=.5) +
    scale_y_continuous("PSE (ms)", 
                       breaks = c(0, 15, 30, 45, 60),
                       limits = c(-10, 70)) +
    scale_x_discrete("Condition", 
                     labels = c("Voluntary", "No action", "Difference"))
```

```{r, echo=F}
e2p5 <- grid.arrange(
    e2p3 + 
        ggtitle("A)") +
        theme(plot.margin = unit(c(3,2,3,3), "mm"),
              title = element_text(vjust=-.2, hjust=-.1),
              axis.title = element_text(vjust=0.5, hjust=.5)),
    e2p4 + 
        ggtitle("B)") +
        theme(plot.margin = unit(c(3,3,3,2), "mm"),
              title = element_text(vjust=-.2, hjust=-.15),
              axis.title = element_text(hjust=.5)),
    widths = c(.65, .35))
```

```{r, echo=F}
bind_cols(exp2, as_tibble(fitted(exp2b))) %>%
    ggplot(aes(x=interval, y=k/n, fill=condition)) +
    scale_color_manual(values = color_vals) +
    geom_point(aes(col=condition)) +
    geom_ribbon(aes(ymin=`2.5%ile`/n, ymax=`97.5%ile`/n), alpha = .3) +
    geom_line(aes(y=Estimate/n, col=condition)) +
    facet_wrap("id")
```

# Experiment 3

```{r}
( exp3 <- filter(illusion, exp == 3) )
```

```{r, echo=F}
e3p1 <- exp3 %>% 
    filter(exclude == FALSE) %>%
    ggplot(aes(x=interval, y=k/n, col=condition)) +
    scale_color_manual(values = color_vals) +
    geom_line(size=.5) +
    geom_point() +
    scale_y_continuous(breaks=c(0, 0.5, 1),
                       labels=c("0", ".5", "1")) +
    labs(x="Inter-stimulus interval (ms)", y="Perceived element motion") +
    facet_wrap(~id, nrow=6)
e3p2 <- e3p1 %+% filter(exp3, exclude == TRUE) + 
    theme(aspect.ratio = 1)
grid.arrange(
    e3p1 + ggtitle("A)"),
    e3p2 + ggtitle("B)") +
        theme(axis.title = element_text(colour = "white"),
              axis.text = element_text(colour = "white")),
    widths = c(8, 2))
```

We reject the participants in B.

```{r, echo=F}
exp3 <- filter(exp3, exclude == F)
exp3$isic <- ( exp3$interval - Cc ) / 10
```

### GLMM MLE estimation

```{r, eval = F}
exp3mle <- glmer(k/n ~ isic*condition + (isic*condition|id),
                 weights = n, family=binomial(link=logit), 
                 data=exp3)
```

```{r}
summary(exp3mle)
```

### GLMM Bayes estimation

```{r, eval = F}
exp3b <- brm(k | trials(n) ~ isic*condition + (isic*condition|id),
             family=binomial(link=logit), prior = Priors,
             data=exp3, cores = 4, iter = iters, warmup = warmups)
```

```{r, echo=F}
print(exp3b$fit, pars = Pars, probs = c(0.025, 0.975), digits=3)
```

```{r}
# Posterior probability (one-sided p-value)
mean(posterior_samples(exp3b, pars = "b_cond") > 0) * 100
```

```{r, echo=F}
post <- posterior_samples(exp3b, pars = "b")
exp3pse <- tibble(
    Involuntary = get_pse(post, 0, Cc, 10),
    Voluntary = get_pse(post, 1, Cc, 10)) %>%
    mutate(Difference = Voluntary - Involuntary) %>%
    gather()
exp3psesum <- group_by(exp3pse, key) %>%
    summarise(m = mean(value),
              lwr = quantile(value, probs=.025),
              upr = quantile(value, probs=.975))
exp3psesum
group_by(exp3pse, key) %>%
    summarize(pp = mean(value > 0))
```

### Plot results

```{r, message=F, echo=F}
e3p3 <- expand.grid(
    isic = seq(min(exp3$isic), max(exp3$isic), length = 32),
    n = 1,
    condition = c("involuntary", "voluntary")) %>%
    bind_cols(., fitted(exp3b, 
                        newdata = ., 
                        re_formula=NA, 
                        scale = "response") %>%
                  as_tibble()
              ) %>%
    mutate(interval = 10*isic + Cc) %>%
    as_tibble() %>%
    ggplot(aes(x=interval)) +
    scale_color_manual(values = color_vals) +
    scale_fill_manual(values = color_vals) +
    geom_ribbon(aes(ymin=`2.5%ile`, 
                    ymax=`97.5%ile`, 
                    fill=factor(condition)),
                alpha=alphas, col=NA) +
    geom_line(aes(y=Estimate, col=factor(condition), lty=factor(condition)),
              size=1.35) +
    scale_x_continuous(breaks = sort(unique(exp3$interval)),
                       expand = c(0, 0.001)) +
    scale_y_continuous(breaks = c(0, .25, .5, .75, 1),
                       labels = c("0", ".25", ".5", ".75", "1"),
                       limits = c(0, 1), expand = c(0, 0.001)) +
    labs(x="Inter-stimulus interval (ms)", y="Pr(element motion)") 
```

```{r, echo=F}
e3p4 <- ggplot(exp3psesum, aes(x=reorder(key, rev(m)), m)) +
    geom_hline(yintercept = 0, lty=2) +
    geom_point(size=2) +
    geom_errorbar(aes(ymin=lwr, ymax=upr), width = .2, size=.5) +
    scale_y_continuous("PSE (ms)", 
                       breaks = c(0, 15, 30, 45, 60),
                       limits = c(-10, 70)) +
    scale_x_discrete("Condition", 
                     labels = c("Voluntary", "No action", "Difference"))
```

```{r, echo=F}
e3p5 <- grid.arrange(
    e3p3 + 
        ggtitle("A)") +
        theme(plot.margin = unit(c(3,2,3,3), "mm"),
              title = element_text(vjust=-.2, hjust=-.1),
              axis.title = element_text(vjust=0.5, hjust=.5)),
    e3p4 + 
        ggtitle("B)") +
        theme(plot.margin = unit(c(3,3,3,2), "mm"),
              title = element_text(vjust=-.2, hjust=-.15),
              axis.title = element_text(hjust=.5)),
    widths = c(.65, .35))
```


```{r, echo=F}
bind_cols(exp3, as_tibble(fitted(exp3b))) %>%
    ggplot(aes(x=interval, y=k/n, fill=condition)) +
    scale_color_manual(values = color_vals) +
    geom_point(aes(col=condition)) +
    geom_ribbon(aes(ymin=`2.5%ile`/n, ymax=`97.5%ile`/n), alpha = .3) +
    geom_line(aes(y=Estimate/n, col=condition)) +
    facet_wrap("id")
```


# Experiment 4

```{r}
( exp4 <- filter(illusion, exp == 4) )
```

```{r, echo=F}
e4p1 <- exp4 %>% 
    filter(exclude == FALSE) %>%
    ggplot(aes(x=interval, y=k/n, col=condition)) +
    scale_color_manual(values = color_vals) +
    geom_line(size=.5) +
    geom_point() +
    scale_y_continuous(breaks=c(0, 0.5, 1),
                       labels=c("0", ".5", "1")) +
    labs(x="Inter-stimulus interval (ms)", y="Perceived element motion") +
    facet_wrap(~id, nrow=6)
e4p2 <- e4p1 %+% filter(exp4, exclude == TRUE) + 
    theme(aspect.ratio = 1)
grid.arrange(
    e4p1 + ggtitle("A)"),
    e4p2 + ggtitle("B)") +
        theme(axis.title = element_text(colour = "white"),
              axis.text = element_text(colour = "white")),
    widths = c(8, 2))
```

We reject the participants in B.

```{r, echo=F}
exp4 <- filter(exp4, exclude == F)
exp4$isic <- ( exp4$interval - Cc ) / 10
```

### GLMM MLE estimation

```{r, eval = F}
exp4mle <- glmer(k/n ~ isic*condition + (isic*condition|id),
                 weights = n, family=binomial(link=logit), 
                 data=exp4)
```

```{r}
summary(exp4mle)
```

```{r newstuff}
table(exp4$id)
```

### GLMM Bayes estimation

```{r, eval = F}
exp4b <- brm(k | trials(n) ~ isic*condition + (isic*condition|id),
             family=binomial(link=logit), prior = Priors,
             data=exp4, cores = 4, iter = iters, warmup = warmups)
```

```{r, echo=F}
Pars <- parnames(exp4b)[1:4]
print(exp4b$fit, pars = Pars, probs = c(0.025, 0.975), digits=3)
```

```{r}
# Posterior probability (one-sided p-value)
mean(posterior_samples(exp4b, pars = "b_cond") > 0) * 100
```

```{r, echo=F}
post <- posterior_samples(exp4b, pars = "b")
exp4pse <- tibble(
    `No Warning` = get_pse(post, 0, Cc, 10),
    Warning = get_pse(post, 1, Cc, 10)) %>%
    mutate(Difference = Warning - `No Warning`) %>%
    gather()
exp4psesum <- group_by(exp4pse, key) %>%
    summarise(m = mean(value),
              lwr = quantile(value, probs=.025),
              upr = quantile(value, probs=.975))
group_by(exp4pse, key) %>%
    summarize(pp = mean(value > 0))
exp4psesum
exp4psesum$key <- factor(exp4psesum$key, 
                         levels = c("Warning", "No Warning", "Difference"))
```

### Plot results

```{r, message=F, echo=F}
e4p3 <- expand.grid(
    isic = seq(min(exp4$isic), max(exp4$isic), length = 32),
    n = 1,
    condition = c("warning", "no_warning")) %>%
    bind_cols(., fitted(exp4b, 
                        newdata = ., 
                        re_formula=NA, 
                        scale = "response") %>%
                  as_tibble()
              ) %>%
    mutate(interval = 10*isic + Cc) %>%
    as_tibble() %>%
    ggplot(aes(x=interval)) +
    scale_color_manual(values = color_vals) +
    scale_fill_manual(values = color_vals) +
    geom_ribbon(aes(ymin=`2.5%ile`, 
                    ymax=`97.5%ile`, 
                    fill=factor(condition)),
                alpha=alphas, col=NA) +
    geom_line(aes(y=Estimate, col=factor(condition), lty=factor(condition)),
              size=1.35) +
    scale_x_continuous(breaks = sort(unique(exp4$interval)),
                       expand = c(0, 0.001)) +
    scale_y_continuous(breaks = c(0, .25, .5, .75, 1),
                       labels = c("0", ".25", ".5", ".75", "1"),
                       limits = c(0, 1), expand = c(0, 0.001)) +
    labs(x="Inter-stimulus interval (ms)", y="Pr(element motion)") 
```

```{r, echo=F}
e4p4 <- ggplot(exp4psesum, aes(x=key, m)) +
    geom_hline(yintercept = 0, lty=2) +
    geom_point(size=2) +
    geom_errorbar(aes(ymin=lwr, ymax=upr), width = .2, size=.5) +
    scale_y_continuous("PSE (ms)", 
                       breaks = c(0, 15, 30, 45, 60),
                       limits = c(-10, 70)) +
    scale_x_discrete("Condition")
```

```{r, echo=F}
e4p5 <- grid.arrange(
    e4p3 + 
        ggtitle("A)") +
        theme(plot.margin = unit(c(3,2,3,3), "mm"),
              title = element_text(vjust=-.2, hjust=-.1),
              axis.title = element_text(vjust=0.5, hjust=.5)),
    e4p4 + 
        ggtitle("B)") +
        theme(plot.margin = unit(c(3,3,3,2), "mm"),
              title = element_text(vjust=-.2, hjust=-.15),
              axis.title = element_text(hjust=.5)),
    widths = c(.65, .35))
```


```{r, echo=F}
bind_cols(exp4, as_tibble(fitted(exp4b))) %>%
    ggplot(aes(x=interval, y=k/n, fill=condition)) +
    scale_color_manual(values = color_vals) +
    geom_point(aes(col=condition)) +
    geom_ribbon(aes(ymin=`2.5%ile`/n, ymax=`97.5%ile`/n), alpha = .3) +
    geom_line(aes(y=Estimate/n, col=condition)) +
    facet_wrap("id")
```

# Combined analysis

We also compared the effect of condition across the Ternus experiments using an interaction term. That is, is the effect of condition greater in experiments 2 and 3, than in experiment 4?

```{r}
( fulldata <- illusion %>% filter(exp > 1, !exclude) )
fulldata$isic <- ( fulldata$interval - Cc ) / 10
```

## GLMM MLE Estimation

```{r}
fullmle <- glmer(k/n ~ isic*cond + exp*isic + exp*cond +
                     (isic*cond|id),
                 weights=n, family=binomial(link=logit), 
                 data=fulldata)
```

```{r}
summary(fullmle)
```

## GLMM Bayes estimation

```{r, eval = F}
fullb <- brm(k | trials(n) ~ isic*cond + exp*isic + exp*cond +
                 (isic*cond|id),
             family=binomial(link=logit), prior = Priors,
             data=fulldata, cores = 4, iter = iters, warmup = warmups, 
             save_ranef = FALSE)  # Save space

```

```{r, echo=F}
Pars <- parnames(fullb)[1:10]
summary(fullb, pars = Pars)
```

Posterior probability that effect of condition (i.e. warning condition effect is smaller than voluntary action condition effect).

```{r}
# Posterior probability (one-sided p-value)
mean(posterior_samples(fullb, pars = "b_cond:exp4") < 0) * 100
```

Compare effect of condition across the three Ternus experiments:

```{r}
x <- as.data.frame(fullb, pars = "b_cond") %>% 
    as_tibble() %>% 
    transmute(cond_exp2 = b_cond,
              cond_exp3 = b_cond + b_cond.exp3,
              cond_exp4 = b_cond + b_cond.exp4,
              cond_2v3 = b_cond.exp3,
              cond_2v4 = b_cond.exp4,
              cond_3v4 = cond_exp4 - cond_exp3)
x %>% 
    gather() %>% 
    group_by(key) %>% 
    summarize(bhat = mean(value),
              `2.5%ile` = quantile(value, probs = 0.025),
              `97.5%ile` = quantile(value, probs = 0.975))
```


```{r, echo = F, eval = F}
# Save models in a file
save(exp1b, exp2b, exp3b, exp4b, fullb, ieb,
     exp1mle, exp2mle, exp3mle, exp4mle, fullmle, iemle,
     file="~$models.rda", compress = "bzip2")
```




```{r, echo=F, eval=F}
# Create PDFs of plots
# Don't evaluate with knit--crashes
pdf(file = "exp1combo.pdf", width = 7, height = 5)
plot(e1p5)
dev.off()

pdf(file = "exp1ie.pdf", width = 7, height = 5)
plot(e1bp7)
dev.off()

pdf(file = "exp2combo.pdf", width = 7, height = 5)
plot(e2p5)
dev.off()

pdf(file = "exp3combo.pdf", width = 7, height = 5)
plot(e3p5)
dev.off()

pdf(file = "exp4combo.pdf", width = 7, height = 5)
plot(e4p5)
dev.off()
```
